The limits of self commitment and private paternalism \thanks{}

### 2022-02-26 donde.tex
apr update and tot_tut analysis

Additional evidence of the importance of paternalism in pawnshop commitment is provided by two additional study arms offering variants of `soft' commitment.  In one arm all borrowers were asked to commit to make three monthly payments instead of a single balloon payment, but no external reminders or fees were imposed.  In a second borrowers were given the ability to choose whether to engage in this form of soft commitment.  Both of these arms are completely ineffective, suggesting that it is the combination of external imposition of the contract along with the teeth provided by the reminder and fees that generate the savings to borrowers relative to the status quo contract.

@@

Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.   One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report in our baseline survey that they anticipate recovering the pawn at the time they take the loan.   High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer. Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, costumer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.

@@

\subsection{Measurement of the Cost to Pawning} \label{Data}

@@

In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5 minute survey \textit{before} going to the teller window to appraise their piece and before they were told contract terms (i.e. before treatment status was known). It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 10,437 clients, and the survey response rate is 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}. 
%Survey response rate is 78\%, and response is not related to admin data observables (details in Table \ref{balance_response} in the Appendix).

%We worked in 6 branches of Lender $P$, of differing size and location, although for ease of implementation all of them in Mexico city. For these 6 branches we have two types of data, administrative data and survey data we collected for the experiment.

@@

% Empirically, attrition was not a problem. Table \ref{SS} shows that the number of pawns per branch per day across treatment arms is statistically identical. The last column of the table displays the p-value of an $F$ test of equality of means across arms and shows we cannot reject equality for any of the variables (p-value=0.38 for the number of pawns per day per branch). There is no evidence for selection across treatment arms for any of the admin or survey variables.

%One concern was that after learning the conditions of the contract, clients could decide not to pawn. If they were deferentially responsive to the different conditions, we could end up having different kinds of clients in the different arms. It turns out this was not the case.

@@

%First, we cannot reject that the number of pawns per branch-day is the same across arms (Panel A). Panel C shows that about 98\% of people who answered our baseline survey also pawned, and that this ratio is balanced across arms. Second, not only are the number and shares of pawns the same across arms, but also the characteristics of clients and their pawned pieces are statistically the same across arms. Panel A of Table \ref{SS} tests this with administrative data, while

@@

the comparison of the \textit{Commitment Choice} arm to the \texit{Control} arm provides the test of self-selection that is standard in the behavioral literature.  A lack of impact in this comparison would be consistent either with a population of neo-classical borrowers, for whom the commitment feature is superfluous, or with a population of time-inconsistent borrowers who lack sophistication over their own behavioral problems.  The key to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the comparison of the \textit{Forced Commitment} arm to the \textit{Control}.  So while the forcing of commitment cuts against the grain of a behavioral literature that has largely promoted `nudges', it reveals important additional information that will be particularly relevant in borrower populations that are both hyperbolic and naive.

As a starting point for the empirical analysis, in the Choice arm only 11\% of individuals offered the product selected it. This is initial evidence either that we are dealing with a population of largely time consistent individuals who do not need commitment, or of a population with many naive individuals who do not know that they need it.  If this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.  Deviations between the impacts of these two arms therefore are implicitly a test of the optimality of the choices made in the choice arm.

We pose this question using the standard Intention to Treat analysis equation (\ref{basic_reg}) across arms.

@@

\noindent where $i$ refers to client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Fixed or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment. Results are robust to excluding them. In the regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} We cluster errors at the branch-day level. %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{FC_def}, which we further decompose into its component costs:  payments to capital, fees, interest, and the cost of losing the pawn.  We then cast each of these costs as an Annual Percentage Rate (APR).  as well as an indicator variable for client $i$ losing her pawn. In this subsection $T_{i}$ is an indicator for $i$ having got the \textit{fee-forcing} contract, and $\beta$ estimates the average treatment effect.%\footnote{This is an ATE and not just an ITT since take up of treatment is 100\%.}

@@

The Intention to Treat (ITT) results, presented in Table \ref{main_impact_table} and graphically in Figure \ref{main_te}, are extremely stark.  The Choice arm fails to deliver improvements on any measure (with the exception of an increase in fees, for which we are very powered since this outcome is always zero in the control).  In sharp contrast, the Forced Commitment arm yields very strongly significant decreases in the financial cost of loans to clients.  Despite causing a 106 peso increase in payments to capital and a 28 peso increase in fees, the Forced arm leads to a 100 peso decline in interest payments and an enormous decline in the expected pawn losses (almost 500 pesos), driven by a 12\% decrease in the probability of default.  The bottom panel of the figure casts these costs as APRs, and shows that while the Choice arm actually leads to a slight \textit{increase} in the APR, the Forced arm decreases the effective annualized interest rate of pawn lending by 40\%.   Figure \ref{main_te} gives the standardized effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.  Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.

There are other intermediate outcomes that are impacted by being assigned to frequent payments. Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).% Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost. 
Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6). The percentage of the loan paid increases by 8 percentage points on average (column 7). However the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).

While the mechanical financial cost and APR incurred by pawn-shop clients are key outcomes, it is worth deepening the analysis with a set of additional drivers relevant to the subjective costs perceived by borrowers.  Figure \ref{robustness_fc} shows the results of these robustness checks.  First, rather than using the appraised value of the pawn from the lender, we can assess costs using the subjective value of the pawn reported by the borrower.  Second, because the Commitment contract requires more frequent visits to the branch, there are travel costs incurred relative to the status quo payment structure that we can include in the costs of commitment.  For each visit we add the self-reported transport cost plus a whole day's wage, multiplied by the number of visits. Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract, although we lose more than 1/3 of the observations and some precision from missing data on transportation costs. Finally, we can adjust for the fact that the early payment induced by the commitment contract actually reduces the effective liquidity received by borrowers.  Taking the interest rate as the opportunity cost of capital, the interest payments averted are not really `saved' given that the liquidity is itself foregone.  So our final adjustment removes the saved interest payments from the calculation of the benefits across arms.  The figure shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations.

A simple way to move towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.  We consider this outcome in Table \ref{X}.  We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.  The results show that the Choice arm is no more likely to pawn again, which the Forced arm is X\% more likely to take a second loan.  While this appears to be \texit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were so much more likely to have recovered their pawn and hence to be able to pawn it again.  We can explore this possibility in a number of ways.  First, we can consider the probability that the borrower ever takes another loan using a \textit{different} pawn, an outcome that if anything would be biased downward in the Forced arm.  Finally, we can conduct an endogenous sample split and examine the treatment effects within the sample that does, and does not, recover their pawn from the first loan.  Results indicate that . . .

@@

@@

In the pawn lending context, however, the results from the two arms of the study that feature `soft' commitment further reinforce the centrality of externally imposed commitment. 
Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.  %Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one. While in both cases the economically vulnerable demand less, in the case of the Soft Commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the Soft Commitment contract.  This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix). 
Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.   Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles). We see no difference even for the endogenous group that \textit{chose} to promise (squares). This null effect happens not only on average, but also by percentiles (not shown in Figure). There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise. And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount. Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).

@@

@@

@@

A simple way of interrogating the distribution of treatment effects is to use quantile regression.  Benefits are distributed broadly however. Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles. All of them are negative. 
%This motivated us to implement a finer measure of treatment effects. We used  \cite{atheygrf}'s generalized random forests methodology.\footnote{The methodology uses random forests of honest causal trees to estimate personalized treatment effects. The method generates a partition of the space of characteristics $X$, where each element of the partition is a leaf, and each leaf contains treatment and control clients with similar characteristics $x \in X$ which are used to calculate unbiased treatment effects for that leaf. The optimal partition is that which minimizes expected mean squared error of treatment effects predictions out-of-sample.} %The tree is honest because it uses one sample to build the tree and another one to estimate treatment effects within that tree.
%\cite{atheygrf} show that their treatment effects are asymptotically normal, which allows us to construct confidence intervals for our treatment estimate in each leaf.

@@

Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.   $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost. The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece. The second coefficient uses the subjective value of the pawn instead. In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one. That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.

The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.   Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract. Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.
Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.

>>>>

Additional evidence of the importance of paternalism in pawnshop commitment is provided by two additional study arms offering variants of `soft' commitment.  In one arm all borrowers were asked to commit to make three monthly payments instead of a single balloon payment, but no external reminders or fees were imposed.  In a second arm borrowers were given the ability to choose whether to engage in this form of soft commitment.  Both of these arms are completely ineffective, suggesting that it is the combination of external imposition of the contract along with the teeth provided by the reminder and fees that generate the savings to borrowers relative to the status quo contract.

@@

Our context is also one with high borrower default: 60\% of clients lose their pawn in a time span of 230 days from the date of pawning.   One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the loan size for 86\% of clients, (c) among those that lose their pawn 48\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 74\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline our baseline survey at the time they take the loan.  So it does appear that a large share of default is not `planned' in a simple ex-ante sense.  High default could be also detrimental from the lender's point of view since it may reduce the likelihood that the client becomes a return costumer. Lender P was explicitly interested in  partnering with us to investigate whether a frequent payment contract would increase pawn recovery, costumer satisfaction, and repeat borrowing, and to explore whether there was demand for such a contract.

@@

\subsection{Measurement of the Cost to Pawning} \label{costs}

@@

In addition, we had a team of enumerators in each branch collect surveys and clearly explain the contract terms to walk-in clients. The enumerators were inside the branch and asked clients to complete a 5 minute survey \textit{before} going to the teller window to appraise their piece and before they were told contract terms (i.e. before treatment status was known). It was short to avoid discouraging the potential clients from pawning, but at the same time it aimed to measure the following: demographics, proxies for income/wealth, education, self-control problems/present-biased preferences, experience pawning, if family or friends commonly asked for money, how time consuming and costly it was to come to the branch, the subjective probability of recovering the piece that they intended to pawn, the subjective value of their piece in money terms (how much money they would sell it for), among others. We surveyed 10,437 clients, and the survey response rate is 78\%.\footnote{The Appendix \ref{baseline_survey} transcribes the questionnaire in English.} %\footnote{We also surveyed clients before and after the experiment, so our survey covers a larger sample that we are not using in this paper.}.

@@

@@

@@

The comparison of the Commitment Choice arm to the Control arm provides the test of self-selection that is standard in the behavioral literature.  A lack of impact in this comparison would be consistent either with a population of neo-classical borrowers, for whom the commitment feature is superfluous, or with a population of time-inconsistent borrowers who lack sophistication over their own behavioral problems and so do not choose commitment even though they would benefit from it.  The key to distinguishing these two stories is the treatment effect of commitment on those who would not choose it; this counterfactual is revealed through the additional impact of the Forced Commitment arm over the Choice arm.  So while the forcing of commitment cuts against the grain of a behavioral literature that has largely promoted `nudges', it reveals important additional information that may be particularly relevant in borrower populations that are both hyperbolic and naive.

In the Choice arm, only 11\% of individuals offered the product selected it. This is initial evidence either that we are dealing with a population of largely time consistent individuals who do not need commitment, or of a population with many naive individuals who do not know that they need it.  If this self-selection mechanism works perfectly (as it would in a Roy model with all hyperbolics sophisticated) then the Forced and Choice arms will have an identical effect.  Deviations between the impacts of these two arms therefore are implicitly a test of the optimality of the choices made in the choice arm.

We pose these comparative questions using the standard pooled experimental equation (\ref{basic_reg}):

@@

\noindent where $i$ refers to client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects.\footnote{There is a minority of of clients that pawned again and got assigned a different treatment. Results are robust to excluding them, or to using only the first treatment status assigned, as we show later.  In the main regressions we include them and add a dummy indicating clients who has more than one treatment in the experimental period.} We cluster errors at the branch-day level, the unit of treatment assignment. %\footnote{If we restrict ourselves to pieces that fall in a single-arm (64\%), then treatment reduces the financial cost by 5.7\%, increases the likelihood of recovering their pawn by 35\%, and increases the likelihood of repeat business by 66\%.}.
Our main outcome variables $y_{ij}$ are measures of financial cost in pesos as defined in Section \ref{costs}, which we further decompose into its component costs:  payments to capital, fees, interest, and the cost of losing the pawn.  We then cast each of these costs as an Annual Percentage Rate (APR).  as well as an indicator variable for client $i$ losing her pawn.  $\beta^F$ estimates the Average Treatment Effect of the Forced arm (since compliance is 100\%), and  $\beta^C$ the Intention to Treat of the Choice arm (since it is not).

@@

The core results, presented in Table \ref{main_impact_table} and graphically in Figure \ref{main_te}, are extremely stark.  The Choice arm fails to deliver significant changes in any measure (with the exception of an increase in fees, for which we are highly powered since this outcome is always zero in the control).  In sharp contrast, the Forced Commitment arm yields strongly significant decreases in the financial cost of loans to clients.  Despite causing an increase in payments to capital and fees, the Forced arm leads to a sharp decrease in overall costs of borrowing, driven by a 12 percentage point decrease in the probability of default (more than a 25\% reduction off a base of 44\% default).  The bottom panel of the figure casts these costs as APRs, and shows that while the Choice arm actually leads to a slight \textit{increase} in the APR, the Forced arm decreases the effective annualized interest cost of pawn lending by 40 percentage points.  A credit product that has an effective average APR of 249\% in the status quo arm is reduced to a cost of 209\% through the imposition of a more regularized payment structure.

Table \ref{main_impact_table} decomposes the savings from the Forced and Choice arms into their component parts. The Forced arm increases fees very significantly relative to a control mean of 0, but the monetary value of the fees imposed is small (28 pesos).  Payments towards capital also rise by 167 pesos because the arm is so effective at improving the fraction of individuals actually repaying their loans.  Because the regular repayment structure moves the timing of payment forward it saves borrowers an average of 109 pesos in interest costs.  The very large majority of the overall treatment effect, however, stems from the 491 pesos in retained collateral value induced by the falling probability of default.

Figure \ref{main_te} gives the  effect sizes (in standard deviations) of the two main study arms for three outcomes:  default, the financial cost of the loan, and the effective interest rate paid to acquire the borrowed capital.  Very clearly, the Forced arm is significant for all three outcomes, with very substantial treatment effects in magnitudes for default and APR, and the commitment arm is never significant.\footnote{The slight increase in APR for the Choice arm seen in this picture arises from the fact that the APR calculation has the arm-specific loan size in the denominator, and the loans in the Choice arm turn out to be slightly larger on average than the Control.}    In other words, voluntary commitment is ineffective but the use of forced commitment saves the average borrower an amount of money almost twice the APR of a normal US credit card loan.

There are other intermediate outcomes that are impacted by being assigned to frequent payments. Table \ref{mechanisms} shows that the first payment happens 8 days earlier (column 1) in the Forced Commitment arm than in the status quo one, and that the number of payments increases by 0.19 (column 2).% Figure \ref{induced_to_pay_early} in the correlates HTE on financing cost with the HTE time of first payment and shows that those induced to pay earlier are also those that have larger induced reduction in financial cost. 
Treatment effects are concentrated on the intensive margin, as treatment does \textit{not} affect the fraction of clients who pay a positive amount (column 6). The percentage of the loan paid increases by 8 percentage points on average (column 7). However the percentage of the loan paid is not larger for those that end up losing the pawn (first row of column 8).  This last point is critical; this intervention has the potential to do financial harm if it caused individuals to make more payments on loans for which they would end up defaulting.  This result shows that instead what the Forced arm does is allow individuals who would have made partial payment and defaulted to instead recover their pawn.

Can we overturn these results by incorporating additional factors that would explain the subjective choices made by individuals?  We now examine whether features such as the perceived value of the pawn, travel costs, or discounting might alter the story of comparative impact.  Figure \ref{robustness_fc} shows the results of these robustness checks, and the numbers underlying the figure are shown in Table \ref{table_robustness_fc}.  First, rather than using the appraised value of the pawn from the lender, we can assess costs using the subjective value of the pawn reported by the borrower.  Because borrower valuations are both larger on average and much more variable, this adjustment causes the average impact on financial cost to rise, and the impact on APR in standard deviations to shrink, but both remain significant.   Second, because the Commitment contract requires more frequent visits to the branch, there are travel costs incurred relative to the status quo payment structure that we can include in the costs of commitment.  For each visit we add the self-reported transport cost (or the mean if we are missing this from the individual survey) plus a whole day's wage, multiplied by the number of additional visits from Table \ref{mechanisms}. Adding a whole day's wage may exaggerate cost, but we still observe a reduction of this more comprehensive measure of cost caused by the frequent payment contract. Finally, we can adjust for the fact that the early payment induced by the commitment contract actually reduces the effective liquidity received by borrowers.  Taking the interest rate as the opportunity cost of capital, the interest payments averted are not really `saved' given that the liquidity is itself foregone.  So our final adjustment removes the saved interest payments from the calculation of the benefits across arms.  The figure shows the effects of each of these adjustments on the estimate of financial cost and APR, and illustrates that even when we make all of these adjustment simultaneously the Forced arm generates benefits of 0.11 standard deviations, significant at the 95\% level.

Another way to push the analysis towards a consideration of borrower welfare is the conjecture that if clients exposed to the installment contract like it, they will be more likely to come back vis-a-vis those that got status quo contract.\footnote{\cite{Laibson2018} hypothesizes that consumers use ``experienced utility'' as a guide to make future purchases in this way.} This is indeed what we find in the data.  We consider this outcome in Table \ref{repeat_loans}.  We can first ask whether the individual ever takes a loan after the initial study loan, an analysis which is simply experimental.  The results show that the Choice arm is no more likely to pawn again, which the Forced arm is X\% more likely to take a second loan.  While this appears to be \texit{prima facie} evidence of greater satisfaction with the lender, interpretation here is complicated by the fact that they were so much more likely to have recovered their pawn and hence to be able to pawn it again.  We can explore this possibility in a number of ways.  First, we can consider the probability that the borrower ever takes another loan using a \textit{different} pawn, an outcome that if anything would be biased downward in the Forced arm.  Finally, we can conduct an endogenous sample split and examine the treatment effects within the sample that does, and does not, recover their pawn from the first loan.  Results indicate that . . .

@@

\textcolor{red}{A final important robustness check is to consider clients who pawn more than once within the experiment.  38\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.  The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure \citep{abdulkadirouglu2011accountability}.\footnote{That context provides a particularly severe version of the endogenous re-entry problem because only the losers from initial lotteries re-enter subsequent ones.  Our selection problem is less draconian, but still potentially relevant since we do find treatment effects on pace of repayment and of pawning again}  So in Table \ref{multiple_loans} we provide two straightforward robustness checks for the influence of this problem.  Columns 1-2 repeat the main analysis of financial cost and APR using the baseline approach from our main results, including dummies for the order of pawns for an individual, essentially making the identification within-order.  Columns 3-4 drop all loans other than the first, and Columns 5-6 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns. The core treatment effects are robust to any of these ways of handling repeat pawning, and the effect on the APR actually become larger.  }

@@

In the pawn lending context, however, the results from the two arms of the study that feature `soft' commitment further reinforce the centrality of externally imposed commitment. 
Demand for the Soft Commitment contract  is higher than for the Forced Commitment contract by a factor of 3: {31}\% of clients offered a choice between the status quo contract and the Soft Commitment contract chose commitment.  %Interestingly, the set of people who demand the Soft Commitment contract are different from those that demanded the Forced Commitment one. While in both cases the economically vulnerable demand less, in the case of the Soft Commitment those that we classify as present biased, those that report that they frequently fall into temptation buying, and those that ask for reminders of payment are \textit{less} likely to demand the Soft Commitment contract.  This suggests that those taking up the promise commitment are not the ones needing the commitment (see Figure \ref{interactions_takeup} in the Appendix). 
Nonetheless, we find Soft Commitment, whether chosen or induced, to be completely ineffective in this environment.  Table \ref{impact_soft} and  Figure \ref{fc_pro5}(a) finds that assigning clients to the choice-promise condition has a zero effect on financial cost on average (circles). We see no difference even for the endogenous group that \textit{chose} to promise (squares). This null effect happens not only on average, but also by percentiles (not shown in Figure). There is also no effect on pawn recovery on (first coefficient in Figure \ref{fc_pro5}(b)), even for those that themselves choose to promise. And the null effect carries over if we use the definition of recovery in less than 120 days, or for the (endogenous) subgroups that paid a positive amount. Finally, there is no effect on repeat pawning (Figure \ref{reincidence}).

@@

This is not the first paper to find low demand for commitment, however it is the first we know of that can compare choice vs forcing with a money-metric outcome such as loan repayment. The fact that the Forced Commitment contract lowers financial costs for almost all clients, together with the fact that only 11\% choose it must mean that many consumers are choosing contracts with higher financial costs for themselves. We now use several different techniques to shed further light on the idea that the wrong people are choosing commitment.

@@

\subsection{Treatment Effects for Compliers and Non-Compliers}

A unique feature of our design is the randomized assignment to treatment, control, and choice of treatment.  This structure allows us to observe the average value of both the treated and untreated potential outcomes, as well as the selection into treatment that would occur under choice.  A starting point for how to exploit this structure is to apply the logic usually used to estimate the Treatment on the Treated (ToT) to also recover the Treatment on the Untreated (TuT).  This approach assumes nothing about the decision to choose (other than random sampling generating counterfactual compliance rates that would have been the same in every arm), but imposes three exclusion restriction-style assumptions typical of Local Average Treatment Effect (LATE) analysis.  Namely, a) the typical assumption that an individual not choosing the treatment has the same potential outcome as one not offered it, then b) the mirror image assumption for the Forcing arm that an individual forced to take Commitment has the same potential outcome as an individual freely choosing it, and c) no spillovers from chooser to non-choosers in the choice arm.\footnote{\hl{For robustness we also try a Manski-type monotone IV approach with similar results.}}

More formally, let $Z_i$ be the observed, randomly assigned experimental allocation, where $Z_i=0$ denotes the control arm, $Z_i=1$ denotes the Forced arm, and $Z_i=2$ is the Choice arm.  Let $C_i$ be the choice type; $C_i=0$ when individual $i$ does not choose commitment and $C_i=1$ when chooses commitment, observed only in the Choice arm.  A fraction $p$ of individuals chooses the treatment in the Choice arm.  Finally, $D_i = Z_i\times \mathds{1}(Z_i\neq 2) + C_i\times \mathds{1}(Z_i=2)$ is the observed treatment indicator, and $Y(d,z)$ is the potential outcome function for $d=0,1$, and $z=0,1,2$.

To test the difference between gains for choosers versus gains from non-choosers we need to identify $\mathbb{E}[Y_1-Y_0\;|\;C=1]$ (the Treatment on the Treated), and $\mathbb{E}[Y_1-Y_0\;|\;C=0]$ (the Treatment on the Untreated).   The observed outcome in the Choice arm is the weighted average of the treated and untreated outcomes; $p \times\mathbb{E}[Y_1\;|\;C=1] + (1-p)\times\mathbb{E}[Y_0\;|\;C=0]$.  Given assumptions a) and c) above we can recover the ToT from the difference between the Choice and Control arms as is standard, and then symmetrically we can invoke b) and c) to recover the TuT from the difference between the Forced and Choice arms as follows:

\begin{align*}
ToT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid\; C=1]  &=   \frac{\mathbb{E}[Y \;\mid\; Z=2] - \mathbb{E}[Y \;\mid\; Z=0)}{p} \\
TuT \equiv \mathbb{E}[Y_1 - Y_0 \;\mid \;C=0]  &=  \frac{\mathbb{E}[Y \;\mid\; Z=1] - \mathbb{E}[Y \;\mid\; Z=2]}{(1-p)} 
\end{align*}

This estimate of the ToT is the standard one that would result from instrumenting for compliance with the offering of treatment as in \cite{angrist1996identification}.  The TuT is the analogous estimator, which could be recovered in a regression pooling the forced and choice arms and instrumenting for \textit{not} complying with being assigned to the choice arm (for a more formal development, see the appendix).  The advantage of representing the estimands via division of the relevant ITT by the compliance (non-compliance) rate is that it allows us to estimate all the necessary terms from the single pooled regression Equation \ref{basic_reg}, from which the significance levels for the ToT, the TuT, and the difference between them can all be estimated as single-equation F-tests:

$$ToT = \frac{\beta^C}{p}; \hspace{15} TuT = \frac{(\beta^F - \beta^C)}{(1-p)}; \hspace{15} (ToT-TuT) = \frac{\beta^C}{p}- \frac{(\beta^F - \beta^C)}{(1-p)}. $$

Table \ref{tot_tut} shows the results of this analysis.  Across the board, the TuT is greater than the ToT which illustrates that the `wrong' people are choosing commitment in terms of direct financial cost.\footnote{It is worth noting that the statistical power of these estimands is driven by the compliance rate; given our low overall compliance we are better powered to measure the TuT than the ToT, and the power for the difference between the two would be highest with a compliance rate of 50\%.}

\textcolor{red}{Discussion to be fortified with updated table}

@@

We now want to move away from the experimental consideration of the arms as a whole, and dive into the individual heterogeneity to learn more about the relationship between choice and outcomes.  A simple way of interrogating the distribution of treatment effects is to use quantile regression. Figure \ref{qregs} plots treatment effects on financial cost and APR at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentile of the outcome variables for the Forced and Choice arms.  It illustrates that a) there is substantial internal heterogeneity in the Forced arm, meaning that some people benefit from forcing and some do not, and that b) taken as a whole the Choice arm has no significant benefit in any part of the distribution.  Therefore, within the group being forced to take commitment we find large heterogeneity in the impacts.

We can explore the heterogeneity within the Choice arm in a non-experimental but suggestive way by breaking apart the choosers and non-choosers and separately estimating quantile effects relative to the control for these two groups.  This analysis, shown in Figure \ref{qreg_chooser_nonchooser}, plots the quantile effects for the choosers only (circles), and non-choosers only (squares).  It shows two important features of the observed impacts.  First, the non-choosers in the choice arm never look different from the control, as should be the case if the exclusion restriction invoked in the prior section is true.  Second, all of the heterogeneity that exists within the Choice arm arises from within the Chooser group, and this heterogeneity looks qualitatively similar to (although smaller than) the heterogeneity observed in the Forced arm.  This analysis is observational because it splits the data on an endogenous variable (choice), but is nonetheless suggestive that substantial heterogeneity in treatment effects exists for all individuals exposed to the Commitment product, and that there are no obvious violations of the exclusion restrictions around forced versus chosen compliance.

%Benefits are distributed broadly however. Figure \ref{fc_pro2}(b) displays results from quantile regressions at the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles. All of them are negative. 
%This motivated us to implement a finer measure of treatment effects.

@@

%Figure \ref{fc_pro4} digs in more detail into the sources of variation underlying the main effects in Figure \ref{main_te}.   $\beta$ coefficients and their 95\% confidence interval from estimating equation (\ref{basic_reg}) using different definitions of financial cost. The leftmost coefficient corresponds to plugging into the formula of section \ref{FC_def} the appraised gold value of the pawned piece. The second coefficient uses the subjective value of the pawn instead. In both cases we find that being assigned to the Forced Commitment commitment contract causes a large reduction in the financing cost the client incurred, of 9.4\% (\$297) under the first definition and 13.2\% (\$472) under the second one. That is, we find that \textit{charging} clients a late payment decreases total \textit{fee-inclusive} financing cost.

%The hollow circles in Figure \ref{fc_pro4}(a) show zero average effects for the different definitions of financial cost analogous to the ones described above.   Figure \ref{fc_pro4}(b) shows further that the null effect happens for the 15$^{th}$, 25$^{th}$, 50$^{th}$ 75$^{th}$, and 85$^{th}$ percentiles.\footnote{The few clients that chose the Commitment contract (the solid black squares) do enjoy cost savings of 1005 MXN, which compares favorably to the 304 MXN in the Forced arm (as a fraction of the loan the numbers are 41.5\% and 12.5\%), but this combines the selection and treatment effects.} %Figure \ref{heterogeneous_te_4} plots the distribution of treatment effects and finds that the distribution offering choice actually \textit{increased} financial cost and default for about half of clients compared to being assigned the status-quo contract. Those tended to be the less economically vulnerable and more educated, {women}, and those whose family typically asks them for money.Figure \ref{fc_pro4}(c) finds null effects for pawn recovery. Consistent with these findings, Figure \ref{reincidence} finds no effect on repeat purchases for the Commitment Choice group.
